SubsidyExplorer - Step 0: Data Wrangling

### 2020-03-13 scripts/01_data_wrangling.Rmd
end of day

For the two datasets in this section, we'll export tidied versions individually for use in SubsidyExplorer.

@@

For the four datasets in this section, we'll export a single aggregated demographic dataset for use in SubsidyExplorer.

@@

>>>>

@@

@@

# Section 3 - Fisheries Data

## Fisheries landings for 2000-2017 from the FAO Global Capture Production database (2019)
